\blue{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media - change the title to something close to the main topic of the manuscript ... something with viscous flow instability or viscous fingering)}

### 2017-05-07 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Updates: starting revising Introduction

Due to complex and/or heterogeneous geological formations, detailed modelling and simulation of multiphase flows through porous media is crucial to understand the aforementioned processes. Description of physics and mechanisms of multiphase flows were reported by \citet{wooding_1976} with focus on capillary pressure and the flow regimes in capillary media. A comprehensive review of mechanisms of fingering (i.e., fluid instability) and forces acting on the interface between two immiscible fluids can be found in \citet{homsy_1987}. \citet{adler_1988} described both microscopic and macroscopic scale darcy-equations \red{(BE MORE SPECIFIC ON THEIR CONTRIBUTION TO THE STATE-OF-THE-ART OF THE FIELD!!)}. Nevertheless we should refer to the area of flow instabilities  as these, first described by \citet{saffman_1958}. The first distinction should be made between microscopic and macroscopic instabilities. Microscopic instabilities describe phenomena occurring locally, for example, Kelvin-Helmholtz and Saffman-Taylor instabilities \citep{saffman_1959}. On the other hand the macroscopic instabilities involves two-phase flow system \citep{bottoni_1992}. This paper will focus on microscopic instabilities and phenomena for a two-phase system. A local flow instability that is the focus of this work is due to viscous and stress forces and often named as viscous instabilities or \textit{viscous fingering}.

\medskip
In large scale field oil and gas operations, viscous or density fingers are relatively common in reservoirs with water-injection wells. As water and oil interacts, the interface between these two fluids moves along the geological formation, creating an uneven, or fingered, profile (see Fig.\ref{fig:simple_case}. The result of fingering is an inefficient sweeping efficiency that can bypass significant volumes of recoverable oil and, in severe cases, an early breakthrough of water into adjacent production wellbores. This instability is mainly governed by the ratio of mobility (MR) of the displacing and the displaced fluids (mobility-ratio, MR). %In a water-oil system the MR is given by eq.\ref{eq:MR}.

>>>>

Due to complex and/or heterogeneous geological formations, detailed modelling and simulation of multiphase flows through porous media is crucial to understand the aforementioned processes. Description of physics and mechanisms of multiphase flows were reported by \citet{wooding_1976} with focus on capillary pressure and the flow regimes in capillary media. A comprehensive review of mechanisms of fingering (i.e., fluid instability) and forces acting on the interface between two immiscible fluids can be found in \citet{homsy_1987}. \citet{adler_1988} described both microscopic and macroscopic scale darcy-equations \red{(BE MORE SPECIFIC ON THEIR CONTRIBUTION TO THE STATE-OF-THE-ART OF THE FIELD!!)}. Nevertheless we should refer to the area of flow instabilities  as these, first described by \citet{saffman_1958} \red{(IS THIS TRUE? SAFFMANN MAY HAVE BEEN THE FIRST TO THROUGHLY DISCUSS VISCOUS INSTABILITIES, BUT THERE WERE OTHER SCIENTISTS THAT DESCRIBED FLUID INSTABILITIES BEFORE, E.G., RAYLEIGH(1896), TAYLOR (1955) ETC)}. The first distinction should be made between microscopic and macroscopic instabilities. Microscopic instabilities describe phenomena occurring locally, for example, Kelvin-Helmholtz and Saffman-Taylor instabilities \citep{saffman_1959}. On the other hand, macroscopic instabilities involve two-phase flow system \citep{bottoni_1992}. This paper will focus on microscopic instabilities and phenomena in two-phase systems. A local flow instability that is the focus of this work is due to viscous and stress forces and often named as viscous instabilities or \textit{viscous fingering} \red{(TRY TO MERGE THESE 2 SENTENCES!)}.

\medskip
In oil and gas reservoir exploration, viscous and density fingers are relatively common in reservoirs with water-injection wells. As water and oil interacts, the interface between these two fluids moves along the geological formation, creating an uneven, or fingered, profile (see Fig.\ref{fig:simple_case}. The result of fingering is an inefficient sweeping efficiency that can bypass significant volumes of recoverable oil and, in severe cases, an early breakthrough of water into adjacent production wellbores. This instability is mainly governed by the ratio of mobility (MR) of the displacing and the displaced fluids (mobility-ratio, MR). %In a water-oil system the MR is given by eq.\ref{eq:MR}.
